### 2017-10-25 Draft2/Appending.Dynamic.tex
Remove $$

	$$
	\VarCapacitySeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
	$$
\end{lemma}

@@

\begin{proof}
	The capacity starts out at zero and becomes $\VarInitCapacity$ once one element is appended. From then on, it can only grow by a factor of $\VarGrowthFactor$ via $\FuncGrow$, so if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity. By induction, the rest of the sequence is $$\left\{ \VarGrowthFactor^i\VarInitCapacity \right\}_{i = 1}^k$$ for some $k$. Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $k$ is the smallest integer for which $\VarGrowthFactor^k\VarInitCapacity \geq n$. Using this property, I now derive $k$.

@@

[make lemma]
Now, consider that to grow by $\VarGrowthFactor$, $\FuncGrow$ must be called. So $\VarGrowthFactor^k\VarInitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\VarGrowthFactor^{k - 1}\VarInitCapacity$ for $k \geq 1$. Then $\FuncGrow$ was called at the sizes $$S_R = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil - 1}\VarInitCapacity$$

@@

[ref1]
$$
\FuncWrites(n) = n + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
$$

>>>>

	\begin{align*}
	\VarCapacitySeq = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
	\end{align*}
\end{lemma}

@@

\begin{proof}
	The capacity starts out at zero and becomes $\VarInitCapacity$ once one element is appended. From then on, it can only grow by a factor of $\VarGrowthFactor$ via $\FuncGrow$, so if $\VarGrowthFactor^i\VarInitCapacity$ is the current capacity then $\VarGrowthFactor^{i + 1}\VarInitCapacity$ must be the next capacity. By induction, the rest of the sequence is

	\begin{align*}
	\left\{ \VarGrowthFactor^i\VarInitCapacity \right\}_{i = 1}^k
	\end{align*}

	for some $k$. Since the capacity is only as big as is needs to be, namely greater than or equal to $n$, $k$ is the smallest integer for which $\VarGrowthFactor^k\VarInitCapacity \geq n$. Using this property, I now derive $k$.

@@

[make lemma]
Now, consider that to grow by $\VarGrowthFactor$, $\FuncGrow$ must be called. So $\VarGrowthFactor^k\VarInitCapacity$ being present in $S_C$ means $\FuncGrow$ was called at size $\VarGrowthFactor^{k - 1}\VarInitCapacity$ for $k \geq 1$. Then $\FuncGrow$ was called at the sizes

\begin{align*}
S_R = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil - 1}\VarInitCapacity
\end{align*}

@@

[ref1]
\begin{align*}
\FuncWrites(n) = n + \left( \frac{\VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil} - 1}{\VarGrowthFactor - 1} \right) \VarInitCapacity
\end{align*}
